---
title: "Homework 5"
author: Tianheng Hu
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(patchwork)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate 

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


Create a plot that shows the estimates and CIs for each city 
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```




## Problem 2

This is a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

First, we import datasets

```{r, error=FALSE}
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    data = map(.x = path, ~read_csv(str_c("lda_data/", .x)))) %>% 
  unnest()


long_df = 
  path_df %>% 
  separate(col=path,into=c("arm","id"),sep="_") %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value",
    names_prefix = "week_"
  ) %>% 
    mutate(
    id = gsub("\\.csv", "",id )
  )
long_df
```


Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
long_df %>% 
  ggplot(aes(x = week, y = value, color = id, group = id)) +
  geom_line()+
  facet_grid(~arm) +
  labs(
    x = "Week",
    y = "Value",
    title = "Values over Weeks between Control vs. Experimental Groups"
  ) 



```

From the two plots, within experimental group the values have an increasing trend and the values are constant in the control group. There are more fluctuations in values over different weeks in control group then experimental group.



# Problem 3

Conduct a simulation of t test for mean when population mean is 0.

```{r}
set.seed(1234)
sim_ttest = function(mu) {
  
  sim_data = 
    tibble(
    x = rnorm(n = 30, mean = mu, sd = 5),
  ) 
  
  sim_data%>% 
    t.test(mu = 0, alternative = 'two.sided',conf.level = 0.95) %>%
    broom::tidy() %>% 
    select(estimate, p.value)
}


# generate results of 5000 datasets
sim_results =
  rerun(5000, sim_ttest(mu = 0)) %>% 
  bind_rows() 

```

Repeat the above for μ={1,2,3,4,5,6}.
```{r}
sim_results_mu =
  tibble(
    mu = c(0,1,2,3,4,5,6)
  ) %>% 
  mutate(
    output_lists = map(.x = mu, ~ rerun(5000, sim_ttest(mu = .x))),
    estimate_df = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df) %>% 
  mutate(reject = ifelse(p.value<0.05, "reject","don't reject"))

```


Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r}

sim_results_mu %>% 
  group_by(mu) %>% 
  summarize(
    n=n(),
    prop = sum(reject == "reject")/n) %>% 
  ggplot(aes(x = mu, y = prop))+
    geom_point()+
    geom_line() +
  labs(
    x = "true mean",
    y = "prop of times the null was rejected",
    title = "Values over Weeks between Control vs. Experimental Groups"
  ) 



```

From the plot, the effect size which is the different between true mean and null increases, the proportion of times the null was rejected increases. So effect size and power has a positive association. 


Make a plot showing the average estimate of μ̂  on the y axis and the true value of μ on the x axis.
```{r}
all_plot=
sim_results_mu %>% 
  group_by(mu) %>% 
  summarise(avg_estimate = mean(estimate)) %>% 
  ggplot(aes(x = mu, y = avg_estimate)) +
  geom_point() +
  geom_line() +
    labs(
    x = "true mean",
    y = "average estimate",
    title = "Average Estimate vs True mean"
  ) 
  

```




Make a second plot (or overlay on the first) the average estimate of μ̂  only in samples for which the null was rejected on the y axis and the true value of μ on the x axis.


```{r}
subset_plot = 
sim_results_mu %>% 
  filter(reject == "reject") %>% 
  group_by(mu) %>% 
  summarise(avg_estimate = mean(estimate)) %>% 
  ggplot(aes(x = mu, y = avg_estimate))+
  geom_point() +
  geom_line() +
  labs(
    x = "true mean",
    y = "average estimate",
    title = "Average Estimate vs True mean in those null is rejected"
  ) 
all_plot + subset_plot 
```



For all samples, the average estimate of mean is the same as the true mean. 
However, for those which the null is rejected, the average estimates of mean is a little higher than the true mean when the mu is 1,2 or 3. They become equal to true mean when mu is 4,5 and 6. The reason behind this is that if the power is low the averge estimates will be different from the true mean. This average estimates will approximate the true mean if the power increases. 






